### 2021-07-27 paper/paper.tex
update TODO notes

% TODO: Update Trixi version
As of version v0.3.50 (July 2021), \trixi comes with the following features.
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex/simplex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
  \end{itemize}

@@

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are a lot of (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. They can often be configured in limited amounts by
compile time options and parameter files. In contrast, users of \trixi do not
need to compile anything or learn the syntax of parameter files. They just load
the library and write their simulation setups in Julia. Such scripts describing
a simulation setup for \trixi are called elixirs. As of version v0.3.43, \trixi
comes with \ca 200 example elixirs. A basic elixir could look as follows.

@@

\todo{TODO: Andrew, please describe the setups that you used} %TODO Andrew

@@

@@

\todo{TODO %TODO Summary
\begin{itemize}
  \item Learning a new programming language has some overhead but it pays off
\end{itemize}}

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and Fluxo
  \item The title of our talk at JuliaCon is
  ``Adaptive and extendable numerical simulations with Trixi.jl''.
  Shall we use something like
  ``Adaptive high-order numerical simulations of hyperbolic PDEs with Trixi.jl:
  A case study of Julia for scientific computing'' for this paper?
  \item Restructure non-conservative stuff and add MHD benchmarks
  \item Add new features (Jesse's mesh and solver) to the list and update version, numer of examples, features, \etc
  \item Shall we re-create the schematic overview in tikz?
  \item Shall we compare \trixi to other open source frameworks such as MFEM, NGSolve, DealII, DUNE, FENICS, Firedrake, ClawPack, ...?
  \item Are there other aspects we should discuss?
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}

>>>>

% TODO: Update Trixi version below
As of version v0.3.50 (July 2021), \trixi comes with the following features.
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex/simplex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
  \end{itemize}

@@

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are a lot of (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. They can often be configured in limited amounts by
compile time options and parameter files. In contrast, users of \trixi do not
need to compile anything or learn the syntax of parameter files. They just load
the library and write their simulation setups in Julia. Such scripts describing
a simulation setup for \trixi are called elixirs. As of version v0.3.50, \trixi
comes with \ca 200 example elixirs. A basic elixir could look as follows.
% TODO: Update Trixi version above

@@

\todo{TODO: Andrew, could you please describe the setups that you used? %TODO Andrew
\begin{itemize}
  \item Physical setup
  \item Numerical methods/parameters
  \item Software versions, compiler \etc
  \item Hardware
\end{itemize}}

@@

\todo{TODO: Add MHD results?}

@@

\todo{TODO %TODO Summary
\begin{itemize}
  \item Julia is suited for simulation-focused scientific computing but some
        things need to be improved/demonstrated for HPC
  \item Julia allows us to do some cool stuff in \trixi
  \item Learning a new programming language has some overhead but it pays off
\end{itemize}}

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and FLUXO
  \item The title of our talk at JuliaCon is
  ``Adaptive and extendable numerical simulations with Trixi.jl''.
  Shall we use something like
  ``Adaptive high-order numerical simulations of hyperbolic PDEs with Trixi.jl:
  A case study of Julia for scientific computing'' for this paper?
  \item Restructure non-conservative stuff and add MHD benchmarks
  \item Shall we re-create the schematic overview in tikz?
  \item Shall we compare \trixi to other open source frameworks such as MFEM, NGSolve, DealII, DUNE, FENICS, Firedrake, ClawPack, ...?
  \item Are there other aspects we should discuss?
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}
